Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-11 paper/paper.tex
references added

\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

@@

% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Spatial visualisations communicate the distribution of statistics over
geographic space. The most common display for spatial data is the
choropleth map. The choropleth map is the common display used to present
aggregated statistics for geographic units such as the population.
Creating a choropleth map involves drawing the administrative boundaries
and filling them with colour to communicate the value of the statistic.
However, using a choropleth map base introduces biases when considering
population related distributions. Many sets of Australian statistical
areas have a large disparity between the smallest and largest units. The
rural communities in Australia operate on a much larger geographic space
than small inner-city communities. When a spatial distribution is
related to the size of the areas, or the population density, the size of
the regions can allow erroneous conclusions to be drawn about the state
of the statistic over the entire population, when presenting the
statistics on a geographic map base. This occurs as large regions filled
with a consistent colour or pattern can draw the attention of map
readers, and small regions are not paid equal attention. An alternative
display can be used to effectively communicate a spatial distribution
for a set of heterogeneous areas. This work aims to show that a hexagon
tile map display is a viable alternative to the geographic map base for
presenting population statistics.

@@

A cartogram transforms the geographic map base. The transformation
begins with a choropleth map, and the values of a statistic such as
population, for each geographic unit. There are several algorithms for
transformation; they involve shifting the boundaries of geographic
units, using the value of the statistic to increase or decrease the area
taken by the geographic unit on the map. The changes to the boundaries
result in cartograms that accurately communicate population by map area
for each of the geographic units. The transformation will keep
boundaries of neighbouring areas connected, but the result is unfamiliar
shapes for each geographic unit.

Alternative displays make the trade off between familiar shapes and
representation of variables using the area of geographic units. The
non-contiguous cartgoram method keeps the shapes of geographic units
intact, and change the size of the shape to communicate the values of
statistics. This method disconnects areas when shrinking boundaries, and
breaks the spatial relationship between areas. However, the empty space
created emphasises the comparative density of the statistic, the
difference between the statistic and the amount of land for each
geographic unit. The Dorling cartogram is another method that does not
retain the boundaries of geographic units. Each unit becomes one circle
on the cartogram display; the circles are sized according to the value
of a the statistic, such as population. The neighbour relationships can
be illustrated by connecting the boundaries of the circles. These
cartogram methods all allow two variables to be shown in the single
display.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/liver-1.pdf}
\caption{The smoothed average of liver cancer diagnoses for Australian
males. The divering colour scheme shows dark blue areas with much lower
than average diagnoses, yellow areas with diagnoses around the
Australian average, orange with above average and red shows diagnoses
much higher than average.}
\end{figure}

@@

Null hypothesis: There is NO relationship between the variables,
Alternative hypothesis: There is a relationship between the variables.

@@

Each Group did not see the same data for both map types. Four simulated
sets of data were generated for each treatment. This will generate
twenty-four lineups (twelve lineups of geographic maps, and twelve
lineups of hexagon tile maps). Participants evaluated twelve lineups,
siz of each map type. For each of the six geographic displays and six
hexagon displays, two of each trend model were shown to participants.

@@

\caption{\label{tab:exp_design}Experimental design.}
\centering
\begin{tabular}[t]{llll}
\toprule
Group & Trend & Choro. & Hex.\\
\midrule
A & NW-SE & 1, 2 & 3, 4\\
A & Three Cities & 1, 2 & 3, 4\\
A & All Cities & 2, 4 & 1, 3\\
B & NW-SE & 3, 4 & 1, 2\\
B & Three Cities & 3, 4 & 1, 2\\
\addlinespace
B & All Cities & 1, 3 & 2, 4\\
\bottomrule
\end{tabular}
\end{table}

@@

Demographics were collected regarding the study participants: - Gender
(female / male / other), - Degree education level achieved (high school
/ bachelors / masters / doctorate / other), - Age range (18-24 / 25-34 /
35-44 / 45-54 / 55+ / other) - Lived at least for one year in Australia
(Yes / No )

@@

Three questions were asked regarding each display: - Plot choice -
Reason - Difficulty

@@

For each of the 12 lineup displays the researchers calculated: -
accuracy: the proportion of subjects who detected the data plot -
efficiency: average time taken to respond

@@

The likelihood of detecting the data plot in the lineup can be modelled
using a linear mixed effects model. The base R (R Core Team
\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
generalised linear models. The model used includes the two main effects
map type and trend model, which gives the fixed effects model to be:

@@

The results will be analysed using a linear mixed effects model, with a
subject random effect to account for differences in individuals. There
will be two main effects: map type and trend model, with an interaction
between them, which gives the fixed effects part of the model to be:

\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between map type and trend model. As the response for
whether the participant detected the data plot is binary, a logistic
link model is used.

The model specifies a logistic link, this means the predicted values
from the \texttt{glm} model should be back-transformed to fit between 0
and 1. They are transformed with the link specified below:

@@

Figure \ref{fig:detection_compare} displays the average detection rates
by type of plot, separately for each trend model. Evaluations on the
same data set are connected by a line segment. For both the Three Cities
and All Cities trend models performance was substantially better for the
hexagon tile map. Viewers detected the data plot substantially more
often with the hexagon tile map. One replicate for the All Cities group,
had similar detection rates for both plot types, and this is discussed
in the supplementary \protect\hyperlink{lineups}{Lineups} section.
Surprisingly, participants could also detect the gradual spatial trend
in the NW-SE group from the hexagon tile map. We expected that the
choropleth map would be superior for the type of spatial pattern, but
the data suggests the hexagon tile map performs slightly better, or
equally as well.

Table \ref{tab:desc_stats} shows the means and standard deviations of
the detection rate for each type of plot and each trend model. This also
gives the standard errors, the smallest standard deviation is the Three
Cities trend model shown in a Choropleth display. This group had a very
small detection rate of 0.038.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
\caption{The detection rates achieved by participants are contrasted
when viewing the four replicates of the three trend models. Each point
shows the probability of detection for the lineup display, the facets
separate the trend models hidden in the lineup. The points for the same
data set shown in a choroleth or haxgon tile map display are linked to
show the difference in the detection rate.}
\end{figure}

@@

\caption{\label{tab:desc_stats}}
\centering
\begin{tabular}[t]{lccc}
\toprule
Type & NW-SE & Three Cities & All Cities\\
\midrule
Choro. & 0.505 & 0.038 & 0.228\\
 & (0.501) & (0.192) & (0.421)\\
Hex. & 0.609 & 0.391 & 0.571\\
 & (0.489) & (0.489) & (0.496)\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{detect_glm1} is a summary of the generalised linear mixed
effects model, testing the effect of plot type and trend model on
detection rate. The results support the summary from Figure
@ref\{detection\_compare\}. All terms are statistically significant.
Overall, the hexagon tile map performs marginally better than the
choropleth for all trend models, which is a pleasant surprise. Detection
rate is lower for the Three Cities and All Cities, than the NW-SE group.
The hexagon tile map has a substantially higher detection rate than the
choropleth for Three Cities and All Cities. XXX Put a number for each of
these.

\begin{tabular}{rcrr}
\toprule
Term & Estimate & Std. Error & P value\\
\midrule
Intercept & 0.02 & 0.17 & 0.896\\
Hex. & 0.46$^{*  }$ & 0.22 & 0.037\\
Three Cities & -3.43$^{***}$ & 0.42 & 0.000\\
All Cities & -1.35$^{***}$ & 0.24 & 0.000\\
Hex:Three Cities & 2.46$^{***}$ & 0.47 & 0.000\\
\addlinespace
Hex:All Cities & 1.17$^{***}$ & 0.33 & 0.000\\
\bottomrule
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
\caption{The distribution of the time taken (seconds) to submit a
response for each combination of trend, whether the data plot was
detected, and type of display, shown using horizontally jittered
dotplots. The coloured point indicates average time taken for each plot
type. Although some participants take just a few seconds per evaluation,
and some take as much as mcuh as 60 seconds, but there is very little
difference in time taken between plot types.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/certainty-1.pdf}
\caption{The amount of times each level of certainty was chosen by
participants when viewing hexagon tile map or choropleth displays.
Participants were more likely to choose a high certainty when
considering a Choropleth map. The mid value of 3 was the default
certainty, it was chosen most for the Hexagon tile map displays.}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{llll}
\toprule
Trend & Detected & Choro. & Hex.\\
\midrule
NW-SE & No & trend & clusters\\
NW-SE & Yes & trend & clusters\\
Three Cities & No & trend & clusters\\
Three Cities & Yes & consistent & clusters\\
All Cities & No & trend & clusters\\
\addlinespace
All Cities & Yes & clusters, consistent & clusters\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{contributors}{%
\subsection{Contributors}\label{contributors}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/contributors-1.pdf}
\caption{The probablity of detection acheived by the contributors in
each group is shown by the points. Group B has a larger range and a
smaller inter-quartile range. Group A and both had 3 people who did not
find any of the data maps in the displays.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/choices-1.pdf}
\caption{Each facet is associated with one lineup, the height of the
points show the proportion of the participants that made each choice
when considering each lineup. The points coloured orange show the map
which contained a trend model, these are the correct choices. The
numbers differentiate the replicates of each trend model and type of map
display. Participants were able to select 0 to indicate they did not
want to choose a map.}
\end{figure}

@@

The demonstrative images of the \texttt{shinydashboard} web application
display the demographic and consent page in Figure \ref{fig:survey1}.

@@

@@

@@

@@

>>>>

\usepackage{longtable,booktabs}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

@@

% Pandoc header
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Spatial visualisations communicate the distribution of statistics over geographic space. The most common display for spatial data is the choropleth map. It is used to present aggregated statistics for geographic units such as the population. Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. However, using a choropleth map base introduces biases when considering population related distributions (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}).
Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
The rural communities in Australia operate on a much larger geographic space than small inner-city communities. When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base. This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention (Griffin \protect\hyperlink{ref-CTTMB}{1980}). An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas (Dent \protect\hyperlink{ref-NISCC}{1972}).
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.

@@

A cartogram transforms the geographic map base. The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit. There are several algorithms for transformation (Dorling \protect\hyperlink{ref-ACTUC}{2011}), (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}); they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units. The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.

Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units. The non-contiguous cartgoram method (Olson \protect\hyperlink{ref-NAC}{1976}) keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics. This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas. However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
The Dorling cartogram (Dorling \protect\hyperlink{ref-ACTUC}{2011}) is another method that does not retain the boundaries of geographic units. Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population. The neighbour relationships can be illustrated by connecting the boundaries of the circles. A similar approach was pioneered by Raisz (\protect\hyperlink{ref-RSCW}{1963}), using rectangles that tile to align borders of neighbours (Monmonier \protect\hyperlink{ref-CDWCS}{2005}).
These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/liver-1.pdf}
\caption{\label{fig:liver}The smoothed average of liver cancer diagnoses for Australian males. The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
\end{figure}

@@

\begin{itemize}
\item
  Null hypothesis: There is NO relationship between the variables,
\item
  Alternative hypothesis: There is a relationship between the variables.
\end{itemize}

@@

Each Group did not see the same data for both map types. Four simulated sets of data were generated for each treatment.
This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \ref{tab:exp-design}.

@@

\caption{\label{tab:exp-design}The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.}
\centering
\begin{tabular}[t]{llll}
\toprule
Group & Trend & Choro. & Hex.\\
\midrule
 & NW-SE & 1, 2 & 3, 4\\
\cmidrule{2-4}
 & Three Cities & 1, 2 & 3, 4\\
\cmidrule{2-4}
\multirow{-3}{*}{\raggedright\arraybackslash A} & All Cities & 2, 4 & 1, 3\\
\cmidrule{1-4}
 & NW-SE & 3, 4 & 1, 2\\
\cmidrule{2-4}
 & Three Cities & 3, 4 & 1, 2\\
\cmidrule{2-4}
\multirow{-3}{*}{\raggedright\arraybackslash B} & All Cities & 1, 3 & 2, 4\\
\bottomrule
\end{tabular}
\end{table}

@@

Demographics were collected regarding the study participants:

\begin{itemize}
\tightlist
\item
  Gender (female / male / other),
\item
  Degree education level achieved (high school / bachelors / masters / doctorate / other),
\item
  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
\item
  Lived at least for one year in Australia (Yes / No )
\end{itemize}

@@

Three questions were asked regarding each display:

\begin{itemize}
\tightlist
\item
  Plot choice
\item
  Reason
\item
  Difficulty
\end{itemize}

@@

For each of the 12 lineup displays the researchers calculated:

\begin{itemize}
\tightlist
\item
  accuracy: the proportion of subjects who detected the data plot
\item
  efficiency: average time taken to respond
\end{itemize}

@@

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
The R (R Core Team \protect\hyperlink{ref-RCore}{2019}) \texttt{glmer()} function in the (Bates et al. \protect\hyperlink{ref-lme4}{2015}) package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

@@

The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:

@@

Figure \ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model. Evaluations on the same data set are connected by a line segment. For both the Three Cities and All Cities trend models performance was substantially better for the hexagon tile map. Viewers detected the data plot substantially more often with the hexagon tile map. One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the supplementary \protect\hyperlink{lineups}{Lineups} section. Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map. We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.

Table \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model. This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display. This group had a very small detection rate of 0.038.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/detect-compare-1.pdf}
\caption{\label{fig:detect-compare}The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models. Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup. The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate.}
\end{figure}

@@

\caption{\label{tab:desc-stats}The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays. The associated standard errors are also included.}
\centering
\begin{tabular}[t]{lccc}
\toprule
Type & NW-SE & Three Cities & All Cities\\
\midrule
Choro. & 0.51 & 0.04 & 0.23\\
 & (0.50) & (0.19) & (0.42)\\
\addlinespace
Hex. & 0.61 & 0.39 & 0.57\\
 & (0.49) & (0.49) & (0.50)\\
\bottomrule
\end{tabular}
\end{table}

\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate. This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
\centering
\begin{tabular}[t]{rrlrr}
\toprule
Term & Est. & Sig. & Std. Error & P val\\
\midrule
Intercept & 0.02 & $^{ }$ & 0.17 & 0.90\\
Hex. & 0.46 & $^{*}$ & 0.22 & 0.04\\
\addlinespace
Three Cities & -3.43 & $^{***}$ & 0.42 & 0.00\\
All Cities & -1.35 & $^{***}$ & 0.24 & 0.00\\
\addlinespace
Hex:Three Cities & 2.46 & $^{***}$ & 0.47 & 0.00\\
Hex:All Cities & 1.17 & $^{***}$ & 0.33 & 0.00\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate. The results support the summary from Figure \ref{fig:detect-compare}. All terms are statistically significant. Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths.

When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03, is extremely low, especially compared to the NW-SE trend. When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.21. The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.38 and All Cities trend 0.58.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
\caption{\label{fig:beeswarm}The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots. The coloured point indicates average time taken for each plot type. Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/certainty-1.pdf}
\caption{\label{fig:certainty}The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays. Participants were more likely to choose a high certainty when considering a Choropleth map. The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}
\end{figure}

@@

\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct.}
\centering
\begin{tabular}[t]{llll}
\toprule
Trend & Detected & Choro. & Hex.\\
\midrule
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
\cmidrule{1-4}
 & No & trend & clusters\\
\cmidrule{2-4}
\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/choices-1.pdf}
\caption{\label{fig:choices}Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.}
\end{figure}

@@

The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Figure
\ref{fig:survey_demogs}.

@@

\hypertarget{contributor-performance}{%
\subsection{Contributor Performance}\label{contributor-performance}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/contributors-1.pdf}
\caption{\label{fig:contributors}The probablity of detection acheived by the contributors in each group is shown by the points. Group B has a larger range and a smaller inter-quartile range. Group A and both had 3 people who did not find any of the data maps in the displays.}
\end{figure}

@@

\leavevmode\hypertarget{ref-NISCC}{}%
Dent, Borden D. 1972. ``A Note on the Importance of Shape in Cartogram Communication.'' \emph{Journal of Geography} 71 (7): 393--401. \url{https://doi.org/10.1080/00221347208981697}.

\leavevmode\hypertarget{ref-ACTUC}{}%
Dorling, Daniel. 2011. ``Area Cartograms: Their Use and Creation.'' In \emph{Concepts and Techniques in Modern Geography (Catmog)}, 59:252--60. \url{https://doi.org/10.1002/9780470979587.ch33}.

\leavevmode\hypertarget{ref-CTTMB}{}%
Griffin, T. L.C. 1980. ``Cartographic Transformation of the Thematic Map Base.'' \emph{Cartography} 11 (3): 163--74. \url{https://doi.org/10.1080/00690805.1980.10438102}.

@@

\leavevmode\hypertarget{ref-CBATCC}{}%
Kocmoud, C, and D House. 1998. ``A Constraint-based Approach to Constructing Continuous Cartograms.'' In \emph{Proc. Symp. Spatial Data Handling}, 236--46.

@@

\leavevmode\hypertarget{ref-CDWCS}{}%
Monmonier, Mark. 2005. ``Cartography: Distortions, World-views and Creative Solutions.'' \emph{Progress in Human Geography} 29 (2): 217--24. \url{https://doi.org/10.1191/0309132505ph540pr}.

\leavevmode\hypertarget{ref-NAC}{}%
Olson, Judy M. 1976. ``Noncontiguous Area Cartograms.'' \emph{The Professional Geographer} 28 (4): 371--80. \url{https://doi.org/10.1111/j.0033-0124.1976.00371.x}.

\leavevmode\hypertarget{ref-RSCW}{}%
Raisz, Erwin. 1963. ``Rectangular Statistical Cartograms of the World.'' Journal Article. \emph{Journal of Geography} 35 (1): 8--10. \url{https://doi.org/10.1080/00221343608987880}.
